% Author: Christian Bagshaw
% Date: August 2020
% Revised: JMS; 22 January 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Divisibility of a Product}

\begin{xca}[Divisibility of a Product]{xca:div-prod}
Let $a,b$ and $c$ be integers. Prove that if $a$ divides $b$, then $a$ divides $bc$. 
\end{xca}

\begin{flaw}{flaw:div-prod} 
Suppose $a$ is even. Since $a$ divides $b$ this means $b$ is even. Therefore $bc$ is even, so that means $a$ divides $bc$. 
\end{flaw}

\clearpage
\subsection{Error classification}

There are multiple errors
 in the Flawed Proof \ref{flaw:div-prod}. 

 
 \begin{description}
    \item[WM]  There is no need to suppose the case that $a$ is even.
    \item[EO-(WM)] The flawed proof has not considered the case where $a$ is odd. 
    \item[N-A] The assertion ``since $a$ divides $b$ this means $b$ is even" requires more details. 
    \item[F-FI] The implication  ``$bc$ is even, so that means $a$ divides $bc$" is false. 
 	
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
    \item Wrong Method (WM)
    \item Error Caused Ommision Wrong Method (EO-(WM))
    \item Novice Assertion (N-A)
	\item 	Fundamental False Implication (F-FI). 
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:div-prod}. 

\begin{prf}{prf:div-prod} 
Suppose that $a,b \in \Z$ and suppose that $a$ divides $b$.
Since $a$ divides $b$, there exists some integer $k$ such that $ak = b$. Multiplying both sides by $c$ gives us that $akc = bc$. We will let $kc = l$, and note that $l$ is an integer. Thus $al = bc$, so by definition $a$ divides $bc$. 

\end{prf}