% Author: Kimberly Golubeva
% Date: 27 July 2020
% Revised: JMS 3 Feb 2020
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Proof by Contrapositive}

\begin{xca}{xca:contra_parity}
Let $x \in \mathbb{Z}.$ Prove that if $x^2-6x+5$ is even, then $x$ is odd.  
\end{xca}

\begin{flaw}{flaw:contra_parity} 
Suppose that $x^2-6x+5$ is even. We want to prove that $x$ is odd. By the definition of even, $x^2-6x+5 = 2k$ for some integer $k.$ So we have $x^2-6x+5 = 2k$ and, rearranging, $x^2-6x+(5-2k) = 0$. Then, using the quadratic formula, 
\begin{align*}
    x &= \frac{6 \pm \sqrt{6^2 - 4(1)(5-2k)}}{2} \\
    &= \frac{6 \pm \sqrt{36 - 20 + 8k}}{2} \\
    &= \frac{6 \pm\sqrt{16 + 8k}}{2}\;.
\end{align*}
Now we must show that $x = \frac{6 \pm\sqrt{16 + 8k}}{2}$ is odd. That is, we must show that $\frac{6 \pm\sqrt{16 + 8k}}{2} = 2j+1$ for some integer $j.$ So
\begin{align*}
    \frac{6 \pm\sqrt{16 + 8k}}{2} &= \frac{1}{2}\left(6 \pm \sqrt{16+8k}\right) \\
    &= \frac{1}{2}\left(6 \pm \sqrt{16}\sqrt{8k}\right) \\ 
    &= \frac{1}{2}\left(6 \pm 4\sqrt{8k}\right) 
\end{align*}
... not enough time to finish.
\end{flaw}

\clearpage
\subsection{Error classification}

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:contra_parity}. 

 
 \begin{description}
 	\item[F-WM:] A direct proof may not be available with elementary methods.  An indirect proof (by contradiction, or proving the contrapositive) will be more effective .
 	\item[F-FS:] $\frac{1}{2}\left(6 \pm \sqrt{16+8k}\right) \neq \frac{1}{2}\left(6 \pm \sqrt{16}\sqrt{8k}\right).$
 	
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
	\item 	Fundamental Wrong Method (F-WM)
	\item Fundamental False Statement (F-FS)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:contra_parity}. 

\begin{prf}{prf:contra_parity} 
We will prove the contrapositive of this statement. That is, we prove that if $x$ is even, then $x^2-6x+5$ is odd. To do so, suppose that $x$ is even and write $x = 2k$ for some integer $k.$ Then
\begin{align*}
    x^2-6x+5 &= (2k)^2 - 6(2k) + 5 \\
    &= 4k^2 - 12k + 5 \\
    &= 2(2k^2-6k+2)+1.
\end{align*}
Now, since $2k^2-6k+2 \in \Z$, it follows that $x^2-6x+5$ is odd. Thus, since the contrapositive is true and it is logically equivalent to  the original statement, we can conclude that the original statement is true.
\end{prf}