% Author: Christian Bagshaw
% Date: August 2020
% Revised: JMS; 22 January 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Logic}

\begin{xca}[Converse of a Statement]{xca:converse-1}
Let $n$ be an integer. Prove or disprove the converse and contrapositive of the following statement:\\

If $n$ is a positive integer, then $n + 3$ is a positive integer. 
\end{xca}

\begin{flaw}{flaw:converse-1}
The converse of the statement is ``if $n+3$ is a positive integer, then $n$ is a positive integer". This statement is true. If $n+3$ is positive we can say $n+3 > 0$, which means $n > 0$, so $n$ is positive. \\

The contrapositive of the statement is ``if $n+3$ is not a positive integer, then $n$ is a positive integer". This statement is false. We will provide a counterexample to show this. If $n = -4$, then $n+3 = -1$ is not a positive integer, but $n = -4$ is also not a positive integer. 
\end{flaw}

\clearpage
\subsection{Error classification}


There are several errors
 in the Flawed Proof \ref{flaw:converse-1}.

 \begin{description}
    \item[F-FI] The implication that $n+3 > 0$ means $n > 0$ is false. 
    \item[WP] ``If $n+3$ is not a positive integer, then $n$ is a positive integer" is not the contrapositive of the statement 
 	
 \end{description}

\subsubsection{Error codes}
\begin{itemize}
	\item 	Fundamental False Implication (F-FI)
	\item Wrong Problem (WP)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:converse-1}. 

\begin{prf}{prf:proof1} 
Let $n\in \Z$.

The converse of the statement is ``if $n+3$ is a positive integer, then $n$ is a positive integer". This statement is false. We will provide a counterexample. Let $n = -1$. We have that $n+3 = 2$ is positive, but $n = -1$ is negative.\\

The contrapositive of the statement is ``if $n+3$ is not a positive integer, then $n$ is not a positive integer". This statement is true. Here is a proof:

Suppose that $n+3$ is not a positive integer. Then $n+3 \leq 0$. This means $n+3 - 3 \leq 0 - 3$, so $n \leq -3 \leq  0$. Therefore $n$ is not a positive integer. 
\end{prf}