% Author: Kimberly Golubeva
% Date: 13 July 2020
% Revised: JMS; 22 January 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{The Rationals}

\begin{xca}{xca:intaddfrac}
Prove or disprove the following statement. For all integers $m$ and $n$, if $m, n > 1$, then $\frac1m + \frac1n$ is not an integer.
\end{xca}

\begin{flaw}{flaw:intaddfrac}
Suppose that $m$ and $n$ are integers and that $m,n > 1$. Since $\frac1m$ is the reciprocal of $m$ and it is not an integer and $\frac1n$ is the reciprocal of $n$ and it is not an integer, then there are no two distinct numbers such that $\frac1m + \frac1n$ can ever be an integer.
\end{flaw}

\clearpage
\subsection{Error classification}


There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:intaddfrac}. 

\subsubsection{Error codes}

\begin{description}
 	%\item[F-FS:] The statement that $\frac1{m}$ implies that $\frac1m$ + $\frac1n$ cannot be an integer is false.
 	\item[C-FI:] The statement that $\frac1{m}$ and $\frac1{n}$ are not integers implies that $\frac1m + \frac1n$ is not an integer is false.
 	%\item[C-OS:] Did not consider the case where $m=n$.
 	\item[F-A:] Asserted the entire result.
 \end{description}


\subsubsection{Error codes}
\begin{itemize}
	%\item 	Fundamental False Statement (F-FS)
	\item   Content False Implication (C-FI)
	%\item   Content Omitted Sections (C-OS)
	\item   Fundamental Assertion (F-A)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:intaddfrac}. 

\begin{prf}{prf:intaddfrac} 
This statement is false. Its negation is: there exist integers $m$ and $n$ so that $m>1$, $n>1$ and $\frac1m + \frac1n$ is an integer. Here's a proof:

Let $m,n = 2$. Then $m,n > 1$ and $\frac1m+ \frac1n = \frac12 + \frac12 = 1 \in \mathbb{Z}.$
\end{prf} 