% Author: Kimberly Golubeva
% Date: 12 Oct 2020
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Compactness}

\begin{xca}{xca:compact_subset}
Show that a non-empty closed subset $S$ of a compact metric space $X$ is compact.
\end{xca}

\begin{flaw}{flaw:compact_subset} %change the label
Suppose that $X$ is compact and that $S \subseteq X$ is closed. We want to show that $S$ is compact. So consider $\{x_n\} \subseteq S.$ By Bolzano Weierstrass, $\{x_n\}$ converges and so it has a converging subsequence. Since $S$ is closed, then it contains all of its accumulation points and so $S$ is sequentially compact.
\end{flaw}

\clearpage
\subsection{Error classification}

%Provide a brief classification and explanation of the errors in the Flawed Proof \ref{flaw:proof1}. %change the label

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:compact_subset}. %change the label


 \begin{description}
 	\item[C-MT:] Misused Bolzano-Weierstrass Theorem.
 	\item[C-FI:] Bolzano-Weierstrass does not give convergence of $\{x_n\}.$
 \end{description}


\subsubsection{Error codes}
\begin{itemize}
	\item 	Content Misusing Theorem (C-MT)
	\item   Content False Implication (C-FI)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:compact_subset}. %change the label

\begin{prf}{prf:compact_subset} %change the label
Let $S$ be a non-empty closed subset of a compact metric space $X$. To show $S$ is compact we will show that each sequence in $S$ has a convergent subsequence whose limit is in $S$. \\

Let $\{x_n\}$ denote a sequence in $S$. Since $X$ is compact and $\{x_n\} \subseteq X,$ we know that $\{x_n\}$ has a convergent subsequence $\{x_{n_k}\}$ converging to $x \in X$. Since $S$ is closed and $\{x_{n_k}\}$ is a convergent sequence in $S$, we must have that $x\in S$. Therefore, $S$ is compact.
\end{prf} 