% Author: Christian Bagshaw
% Date: Oct 2020
%Revised LD April 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Ring Theory}

\begin{xca}[Zero Divisor or Unit]{xca:unit_zerodiv}
Let $R$ be a finite ring with unity. Prove that every element of $R$ is either a unit or a zero divisor.
\end{xca}

\begin{flaw}{flaw:unit_zerodiv} %change the label
Let $r\in R$. Thus by Lagrange's theorem $r^{|R|} = 1$. Thus $r(r^{|R|-1}) = 1$, thus $r$ is a unit.

\end{flaw}

\clearpage
\subsection{Error classification}

%Provide a brief classification and explanation of the errors in the Flawed Proof \ref{flaw:proof1}. %change the label

There is one error
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:unit_zerodiv}.

 \begin{description}
    \item[C-MT] Misuse of Lagrange's theorem.

 	
 \end{description}


\subsubsection{Error codes}
\begin{itemize}
    \item Content Misusing Theorem (C-MT)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:unit_zerodiv}. %change the label

\begin{prf}{prf:unit_zerodiv} %change the label
Let $R$ be a finite ring with unity.
Let $1$ denote the multiplicative identity of $R$. Fix $r \in R$. Consider the map
\begin{align*}
    m_r: R &\to R\\
    x &\mapsto rx.
\end{align*}
We have two possibilities: either $m_r$ is injective or it is not injective. If $m_r$ is injective, then it is also surjective because $R$ is finite. Hence, there exists some $x \in R$ such that $1 = rx$, and thus $r$ is a unit. On the other hand, if $m_r$ is not injective, then there exists $x, x' \in R$ with $x\neq x'$ such that $rx = rx' \: \Rightarrow \: r(x-x') = 0$, and so $r$ is a zero divisor.

\end{prf} 