% Author: Jerrod Smith
% Date: 9 Feb 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{A recursive sequence}

\begin{xca}{xca:label}
	The sequence $\{b_n\}_{n=0}^\infty = \{b_0,b_1,b_2,\ldots\}$ is defined by: $b_0 = 1$, $b_1 = 8$, and for all integers $n\geq 2$, \[b_n = b_{n-1}+2b_{n-2}\]  Prove that $b_n = 3 (2^n) - 2(-1)^n$, for all integers $n\geq 0$.
\end{xca}

\begin{flaw}{flaw:rec-seq-ind} 
Suppose $n$ is a non-negative integer.

\noindent\textbf{Base case}

If $n=0$, then $b_0 = 3(2^0)-2(-1)^0 = 3(1) -2(1) = 3-2=1$.

If $n=1$, then $b_1 = 3(2^1)-2(-1)^2 = 3(2) -2(-1) = 6+2 = 8$.

So the base cases hold.

\noindent\textbf{Induction Hypothesis}

Suppose that for all integers $k\geq 1$, we have $b_m  = 3 (2^m) - 2(-1)^m$, for all integers $0 \leq m \leq k$.

\noindent\textbf{Inductive Step}

We must show that $b_{k+1} = 3 (2^{k+1}) - 2(-1)^{k+1}$.

Since $k+1 \geq 2$, by definition of $b_{k+1}$, we see that
\begin{align*}
	b_{k+1} %& = b_{k+1-1} + 2b_{k+1-2}	\\
			& = b_{k} + 2 b_{k-1} \\
			& = 3 (2^k) - 2(-1)^k + 2[ 3 (2^{k-1}) - 2(-1)^{k-1} ] & (\text{by the induction hypothesis})\\
			%\& = 3(2^k) - 2(-1)^k + 3(2^k) - 4(-1)^{k-1} \\
			%& = 3(2^k) + 3(2^k) - 2(-1)^k -4(-1)^{k-1}\\
			%& = 2\cdot 3(2^k) -2(-1)^{k-1}[(-1) + 2] \\
			%& = 3(2^{k+1}) - 2(-1)^{k-1}(1) \\
			%& = 3(2^{k+1}) - 2(-1)^{k-1}(-1)^2 & (\text{since $1=(-1)^2$})\\ 
			& = 3(2^{k+1}) - 2(-1)^{k+1},
\end{align*}
as required.  

We conclude, by the Principle of Mathematical Induction (Strong Form), that $b_n = 3 (2^n) - 2(-1)^n$, for all integers $n\geq 0$.	


\end{flaw}

\clearpage
\subsection{Error classification}

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:rec-seq-ind}. 

 
 \begin{description}
 	\item[C-A] Result is asserted in the base case.	
 	\item[F-A] Entire result is asserted in the induction hypothesis.
 	\item[N-A] Calculation in inductions step could use more detail.
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
	\item 	 Content Assertion (C-A)
	\item    Fundamental Assertion (F-A)
	\item    Novice Assertion (N-A)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:rec-seq-ind}. 

\begin{prf}{prf:rec-seq-ind} 
Suppose that $n \in \Z$, $n\geq 0$.

\noindent\textbf{Base case:} Consider $n=0$ and $n=1$.
If $n=0$, then \[3(2^n) - 2(-1)^n = 3(1) - 2(1) = 3-2 = 1 = b_0.\]
If $n=1$, then\[3(2^n) - 2(-1)^n = 3(2) - 2(-1) = 6+2 = 8 = b_1.\]

\noindent\textbf{Induction Hypothesis:} Suppose that there exists an integer $k\geq 1$ such that for all integers $m$ if $0 \leq m \leq k$, then $b_m  = 3 (2^m) - 2(-1)^m$.

\noindent\textbf{Inductive Step}

We must show that $b_{k+1} = 3 (2^{k+1}) - 2(-1)^{k+1}$.

Since $k+1 \geq 2$, by definition of $b_{k+1}$, we see that
\begin{align*}
	b_{k+1} & = b_{k+1-1} + 2b_{k+1-2}	\\
			& = b_{k} + 2 b_{k-1} \\
			& = 3 (2^k) - 2(-1)^k + 2[ 3 (2^{k-1}) - 2(-1)^{k-1} ] & (\text{by the induction hypothesis})\\
			& = 3(2^k) - 2(-1)^k + 3(2^k) - 4(-1)^{k-1} \\
			& = 3(2^k) + 3(2^k) - 2(-1)^k -4(-1)^{k-1}\\
			& = 2\cdot 3(2^k) -2(-1)^{k-1}[(-1) + 2] \\
			& = 3(2^{k+1}) - 2(-1)^{k-1}(1) \\
			& = 3(2^{k+1}) - 2(-1)^{k-1}(-1)^2 & (\text{since $1=(-1)^2$})\\ 
			& = 3(2^{k+1}) - 2(-1)^{k+1},
\end{align*}
as required.  

We conclude, by the Principle of Mathematical Induction (Strong Form), that $b_n = 3 (2^n) - 2(-1)^n$, for all integers $n\geq 0$.	

\end{prf}