% Author: Kimberly Golubeva
% Date: 28 September 2020
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Linear Transformations}

\begin{xca}{xca:lin_op_trace}
Let $A$ be an $n \times n$ matrix. Consider $T: \mathbb{R}^{n\times n} \rightarrow \mathbb{R}$ defined by $T(A) = \text{Tr}(A).$ Is $T$ a linear transformation? Explain.
\end{xca}

\begin{flaw}{flaw:lin_op_trace} %change the label
Yes, $T$ is a linear transformation. Consider the following arbitrary $n \times n$ matrices $A$ and $B$ defined as,
$$
  A =
  \begin{bmatrix}
    a & & \\
    & \ddots & \\
    & & y
  \end{bmatrix} \quad , \quad B =
  \begin{bmatrix}
    b & & \\
    & \ddots & \\
    & & z
  \end{bmatrix}
$$

First, we show that Tr$(A+B)=\;$Tr$(A)$ + Tr$(B)$.
\begin{align*}
\text{Tr}(A+B) &= \text{Tr}\left(  \begin{bmatrix}
    a & & \\
    & \ddots & \\
    & & y
  \end{bmatrix} +
  \begin{bmatrix}
    b & & \\
    & \ddots & \\
    & & z
  \end{bmatrix} \right) \\
   &= \text{Tr} \begin{bmatrix}
    a+b & & \\
    & \ddots & \\
    & & y+z
  \end{bmatrix} \\
  &= \text{Tr}(A) + \text{Tr}(B)\;.
  \end{align*}

Next,  we show that Tr$(kA)=\;$ $k$Tr$(A)$.
\begin{align*}
\text{Tr}(kA) &= k\text{Tr}\begin{bmatrix}
    a & & \\
    & \ddots & \\
    & & y
  \end{bmatrix} \\
  &= k\text{Tr}(A)\;.
  \end{align*}
\end{flaw}

\clearpage
\subsection{Error classification}

%Provide a brief classification and explanation of the errors in the Flawed Proof \ref{flaw:proof1}. %change the label

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:lin_op_trace}. %change the label


 \begin{description}
 	\item[N-N:] Denoting the matrix diagonal entries by $a,\ldots,y$ and $b,\ldots, z$ is imprecise. It would be better to denote them by $a_{11}, \ldots, a_{nn}$ and $b_{11},\ldots,b_{nn}$ since these are $n\times n$ matrices.
 
  \item[F-A:] The closed under addition and closed under scalar multiplication portions of the proof are asserted. Indeed, no explanation is given to justify why \[\text{Tr} \begin{bmatrix}
    a+b & & \\
    & \ddots & \\
    & & y+z
  \end{bmatrix} \\
  = \text{Tr}(A) + \text{Tr}(B).\] And similarly, the scalar $k$ is pulled outside of $\mathrm{Tr}(A)$ without justification.
 \end{description}


\subsubsection{Error codes}
\begin{itemize}
	\item Novice Notation (N-N)
	\item   Fundamental Assertions (F-A)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:lin_op_trace}. %change the label

\begin{prf}{prf:lin_op_trace} %change the label
Yes, $T$ is a linear transformation. Let $A=[a_{ij}]$ and $B=[b_{ij}]$ be $n \times n$ matrices and $k \in \mathbb{R}$. \\

First, we will show that $T$ is closed under addition. We have
$$\text{Tr}(A+B) = \sum_{i=1}^n (a_{ii} + b_{ii}) = \sum_{i=1}^n a_{ii} + \sum_{i=1}^n b_{ii} = \text{Tr}(A) + \text{Tr}(B)\;.$$

Next, we will show that $T$ is closed under scalar multiplication. We have
$$\text{Tr}(kA) = \sum_{i=1}^n (ka_{ii}) = k \sum_{i=1}^n a_{ii} = k\text{Tr}(A)\;.$$

\noindent Thus, $T$ is a linear transformation.

\end{prf}
