% Author: Christian Bagshaw
% Date: August 2020
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Similar Matrices}

\begin{xca}[Similar Matrices and Eigenvalues ]{xca:similar_eigen}
Prove similar matrices have the same set of eigenvalues.
\end{xca}

\begin{flaw}{flaw:similar_eigen} %change the label
Since they are similar this means there exists some invertible matrix $P$ such that $A = P^{-1}BP$. The characteristic polynomial for $B$ is given by $\det(B - I\lambda)$. Now making substitutions we can get
\begin{align*}
    \det(B - I\lambda) &= \det(P^{-1}AP - II\lambda)\\
    &= \det(P^{-1}AP) - \det(P^{-1}PI\lambda)\\
    &= \det(P^{-1})\det(A)\det(P) - \det(P^{-1})\det(P)\det(I\lambda)\\
    &= \det(P^{-1})\big{(}\det(A) - \det(I\lambda)\big{)}\det(P)\\
    &= \det(P^{-1})\det(A - I\lambda)\det(P)\\
    &= \det(P)^{-1}\det(P)\det(A - I\lambda)\\
    &= \det(A - I\lambda).
\end{align*}
Thus $\det(A - I\lambda) = \det(B - I\lambda)$, so $A$ and $B$ have the same characteristic polynomial and hence the same eigenvalues.
\end{flaw}

\clearpage
\subsection{Error classification}

%Provide a brief classification and explanation of the errors in the Flawed Proof \ref{flaw:proof1}. %change the label

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:similar_eigen}.

 \begin{description}
    \item[N-O] $A$ and $B$ are not defined.
    \item[N-N] Initially the proof writes $A = P^{-1}BP$, but later the proof makes the substitution $B = P^{-1}AP$.
    \item[C - MT] The flawed proof assumes that determinants distribute over addition/subtraction, which is not the case.
 \end{description}


\subsubsection{Error codes}
\begin{itemize}
	\item Novice Local Omission (N-O)
\item Novice Notation (N-N)
\item Content Misusing Theorem (C-MT)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:similar_eigen}. %change the label

\begin{prf}{prf:similar_eigen} %change the label
Let $A$ and $B$ be similar matrices. We will show that they have the same characteristic polynomial, and hence the same eigenvalues. Since $A$ and $B$ are similar this means there exists some invertible matrix $P$ such that $A = P^{-1}BP$. The characteristic polynomial for $A$ is given by $\det(A - I\lambda)$. Now making substitutions we have
\begin{align*}
    \det(A - I\lambda) &= \det(P^{-1}BP - II\lambda)\\
    &= \det(P^{-1}BP - P^{-1}PI\lambda)\\
    &= \det(P^{-1}BP - P^{-1}I\lambda P)\\
    &= \det(P^{-1}(B - I\lambda)P) \\
    &= \det(P^{-1})\det(B - I\lambda)\det(P) \\
    &= \frac{1}{\det(P)}\det(B - I\lambda)\det(P) \\
    &= \det(B - I\lambda).
\end{align*}
Thus $\det(A - I\lambda) = \det(B - I\lambda)$, so $A$ and $B$ have the same characteristic polynomial and hence the same eigenvalues.
\end{prf} 