% Author: Christian Bagshaw
% Date: August 2020
% Revised: JMS, 22 Feb 2021
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Set Unions and Intersections}

\begin{xca}[De Morgan's Law ]{xca:demorgans}
Let $U$ be a set.
Prove that for all subsets $A$ and $B$ of $U$, $$(A\cup B)^c = A^c \cap B^c.$$
Here $A^c$ denotes the complement of $A$ in $U$, that is $$A^c = U \setminus A = \{x \in U : x \notin A\}.$$
\end{xca}

\begin{flaw}{flaw:demorgans} 
$x \in (A\cup B)^c$ means $x \notin A$ nor $B$ means $x \notin A$ or $x \notin B$ means $x \in A^c $ or $x \in B^c$ means $x \in A^c \cap B^c$. \\

$x \in A^c \cap B^c$ means $x \in A^c $ or $x \in B^c$ means $x \notin A$ or $x \notin B$ means $x \notin A$ nor $B$ means $x \in (A\cup B)^c$. 

\end{flaw}

\clearpage
\subsection{Error classification}
There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:demorgans}. 
 
 \begin{description}
    \item[N-VG] In general, the flawed proof is poorly written. The repetitive use of the word  ``means", and each paragraph being one run on sentence makes it difficult to read. 
    \item[F-FA] The assertion ``$x \notin A$ nor $B$ means $x \notin A$ or $x \notin B$" is incorrect.
    \item[F-FA] The assertion ``$x \in A^c$ or $x \in B^c$ means $x \in A^c \cap B^c$ is incorrect.
    \item[F-FA] The assertion ``$x \in A^c \cap B^c$ means $x \in A^c$ or $x \in B^c$" is incorrect.
    \item [F-FA] The assertion ``$x \notin A$ or $x \notin B$ means $x \notin A$ nor $B$" is incorrect. 
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
	\item Novice Vocabulary Grammar (N-VG)
	\item Fundamental False Assertion (F-FA)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:demorgans}. 

\begin{prf}{prf:demorgans} 
Suppose that $A$ and $B$ are subsets of $U$.  

First, we will prove that $(A\cup B)^c$ is a subset of $A^c \cap B^c$.
Suppose that $x \in (A\cup B)^c$.  That is, $x \in U$ by $x \notin A \cup B$.  Since $x \notin A \cup B$, it follows that $x \notin A$ and $x \notin B$.  By definition of the complement, $x \in A^c$ and $x \in B^c$, and $x \in A^c \cap B^c$.  Thus, $(A\cup B)^c$ is contained in $A^c \cap B^c$.

Now, we will prove that $A^c \cap B^c$ is a subset of $(A\cup B)^c$.  
Suppose that $y \in A^c \cap B^c$.  Then $y \in A^c$ and $y \in B^c$.  That is, $y \in U$ but $y \notin A$ and $y \notin B$.  Moreover, $y \notin A\cup B$.  Thus $y \in (A\cup B)^c$ and $A^c \cap B^c$ is contained in $(A \cup B)^c$.

Therefore, $(A\cup B)^c \subset (A^c \cap B^c)$ and $(A^c \cap B^c) \subset (A\cup B)^c$, which means $(A\cup B)^c = A^c \cap B^c$.
\end{prf}