% Author: Kimberly Golubeva
% Date: 10 August 2020
% Revised: 22 March 2021 JMS
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Composition of Injective Functions}

\begin{xca}{xca:injective_comp}
Recall that ``injective" means ``one-to-one".

\noindent Prove or disprove the following statement. If $f:A \rightarrow B$ and $g:B \rightarrow C$ are injective functions, then $g \circ f : A \rightarrow C$ is injective.
\end{xca}

\begin{flaw}{flaw:injective_comp} 
Suppose that $f:A \rightarrow B$ and $g:B \rightarrow C$ are injective functions. Let $a_1, a_2 \in A$. Then $f(a_1) = f(a_2)$ and so $g(f(a_1)) = g(f(a_2))$. Thus, $g \circ f$ is injective. 
\end{flaw}

\clearpage
\subsection{Error classification}

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:injective_comp}. 

 
 \begin{description}
 	\item[C-VG:] Misunderstanding the definition of what it means for the function $g\circ f: A \rightarrow C$ to be injective.
 	\item[F-A:] Asserted entire result by supposing that $a_1 = a_2.$ 
 	\item[C-LO:] Components of proof are not in logical order due to misuse of the C-VG error. 
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
	\item 	Content Vocabulary and Grammar (C-VG)
	\item   Fundamental Assertions (F-A)
	\item   Content Logical Order (C-LO)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:injective_comp}. 

\begin{prf}{prf:injective_comp} 
Suppose $f:A \rightarrow B$ and $g:B \rightarrow C$ are injective functions. We want to prove that $g \circ f : A \rightarrow C$ is injective. So suppose that $a_1, a_2 \in A$ such that $(g \circ f)(a_1) = (g \circ f)(a_2).$ That is, $g(f(a_1))=g(f(a_2)).$ Since $g$ is injective, it must be the case that $f(a_1)=f(a_2).$ Similarly, since $f$ is injective, we have $a_1=a_2.$ Thus, $g \circ f$ is injective. 
\end{prf}
