% Author: Kimberly Golubeva
% Date: 14 September 2020
% Lauren DeDieu, Jerrod M.~Smith, Kimberly Golubeva and Christian Bagshaw
% A Resource Bank for Writing Intensive Mathematics Courses
% This work is licensed under a  Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License
% http://creativecommons.org/licenses/by-nc-sa/4.0/
\section{Properties of Functions: One-to-one and Onto}

\begin{xca}{xca:onetoone_notonto}
Consider the function $f: \Z \rightarrow \Z$ defined as
$$f(x) = 2x+1\;.$$
Is this function one-to-one? Is it onto? Prove or disprove. 
\end{xca}

\begin{flaw}{flaw:onetoone_notonto} %change the label
This function is one-to-one. Let $a,b \in \Z.$ Suppose that $f(a)=f(b).$ Then,
\begin{align*}
2a + 1 &= 2b + 1 \\
2a &= 2b \\
a &= b\;.
\end{align*}
Thus, $f$ is one-to-one. \\

This function is onto. Let $y \in \Z$. We want to prove that $f(x)=2x+1=y$. Isolating for $x$, we have that $x= \frac{y - 1}{2}$. So choose $x=\frac{y - 1}{2}$. Then $f(x)$ will always equal $y$. Thus, for all $x \in \Z, f(x)= y$ and so $f$ is onto.
\end{flaw}

\clearpage
\subsection{Error classification}

%Provide a brief classification and explanation of the errors in the Flawed Proof \ref{flaw:proof1}. %change the label

There are several errors
% is only one error ... etc.
 in the Flawed Proof \ref{flaw:onetoone_notonto}. %change the label

 
 \begin{description}
 	\item[F-WP:] This proof would be correct if the function was defined on a different domain and codomain. In particular, the function $f$ is both one-to-one and onto when $f: \R \rightarrow \R.$
 	\item[F-FS:] It is not true that $x=\frac{y - 1}{2}$ will always be an integer. 
 \end{description}

 
\subsubsection{Error codes}
\begin{itemize}
	\item 	Fundamental Wrong Problem (F-WP)
	\item   Fundamental False Statement (F-FS)
\end{itemize}
See Section \ref{sec-error} for more information about error classifications.

\clearpage
\subsection{Corrected proof}

The following is a corrected version of Flawed Proof \ref{flaw:onetoone_notonto}. %change the label

\begin{prf}{prf:onetoone_notonto} %change the label
This function is one-to-one. Let $a,b \in \Z.$ Suppose that $f(a)=f(b).$ Then,
\begin{align*}
2a + 1 &= 2b + 1 \\
2a &= 2b \\
a &= b\;.
\end{align*}
Thus, $f$ is one-to-one. \\

This function is not onto. Consider the following counterexample. Choose $y =0$, and assume that there exists $x \in \Z$ such that $f(x)=y.$ Then $f(x)=0 = 2x+1$, which means that $x = \frac{-1}{2}.$ But this is a contradiction since $x = -\frac{1}{2} \notin \Z.$ Thus, for all $x \in \Z, f(x) \neq y$ and so $f$ is not onto.
\end{prf}
